Paper Figures and Text

### 2023-06-09 Fish Data Analysis/NN_Alignment.qmd
Attempted Models of Turning and Distance

ggplot(close_fish_comp %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Yaw.Heading_Diff,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Heading), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Heading-SD_Heading, ymax=Mean_Heading+SD_Heading), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Distance (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

>>>>

ggplot(close_fish_comp %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Yaw.Heading_Diff,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(smaller_dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Heading), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Heading-SD_Heading, ymax=Mean_Heading+SD_Heading), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("Heading Difference (Angle)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

fish_comp_data_combo %>% group_by(Flow, Ablation, Darkness) %>% summarise(n = n())

### 2023-06-09 Fish Data Analysis/Paper_Figures.qmd
Reverting to old files, fixing 3d matching errors
Attempted Models of Turning and Distance

```{r}
school_data <- read.csv("Data/Fish_School_Values_3D.csv")
school_data <- na.omit(school_data)

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

>>>>

```{r}
school_data <- read.csv("Data/Fish_School_Values_3D.csv")

school_data <- na.omit(school_data)

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})
